% Chapter Template

\chapter{Rapid Information Factory Framework (RIFF) - Functional Layer - Transform Superstep} % Main chapter title

\label{Chapter14} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 14. \emph{RIFF - FUNC - Transform}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Main Section 1}

The transform superstep is responsible for transforming the data vault into an enterprise data warehouse. This superstep tranforms the data into knowledge by adding dimensionality and insight to the data vault.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

\subsubsection{Transform Superstep}
\paragraph{The transform superstep uses a series of work cells with an assembly format that is made up out of four components:}
\begin{itemize}
\item{Remote Monitor Yoke}
\item{Input PUPA}
\item{ANT}
\item{Output PUPA}
\end{itemize}
\paragraph{The remote monitoring yoke connects the work cell to the PRISM that controls the spesific factory to enable the communication and control to the PRISM's remote motering yoke to ensure the process is monitored and that it comples it assigned task in the factory.}
\paragraph{The Input PUPA NEST PUPA describes the processsing rules and formats of the data source use as the input to the process. The factory translates the HORUS scripts to generate the processing logic to input the data.}
\paragraph{The ANT is the setup script in HORUS rules that builds a processing engine to process the data form the input PUPA into the processing rules of the output PUPA. }
\paragraph{The output PUPA is the processsing rules and formats of the data source use as the output from the process. The factory translates the HORUS scripts to generate the processing logic to output the data.}

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}

???

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Main Section 2}

???
